Data Exploration: IUCN and AquaMaps

### 2015-10-13 data_explore.Rmd
fixed a ggsave path
adding box plots

ggsave('AreavsPercOverlap_log.png',width=6,height=4)

@@

>>>>

ggsave('figures/AreavsPercOverlap_log.png',width=6,height=4)

@@

## Changes in SPP for scenarios

Comparing three scenarios to the current (v2015) global model for SPP:

* Baseline is: preferring IUCN rangemaps over Aquamaps rangemaps; Aquamaps "presence" threshold is set at 40% or greater.
* Scenario 1: preferring IUCN rangemaps over Aquamaps; AM presence threshold set at >= 1% (effectively, all occurrences).
* Scenario 2: preferring AM maps over IUCN; AM presence >= 40%.
* Scenario 3: preferring AM over IUCN; AM presence >= 1%.

Boxplots:

![Absolute change in SPP score](figures/SPP_scenarios/boxplot_abs_diff.png)

![Relative change in SPP score](figures/SPP_scenarios/boxplot_rel_diff.png)
